Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-11 ms.tex
searching and occupying odes

@@

\subsection{Contest Algorithm}
See Fig. \ref{fig:contests}.
For a defender $x_{def}$ vs an attacker $x_{atk}$, there are 3 stages:
each individual has an aggression trait $a$ and a mass $m$.\\
\begin{equation}\label{eq:logit}
    logit^{-1}(\alpha) = \frac{exp(\alpha)}{1 + exp(\alpha)}
\end{equation}

@@

I am not sure if this is the way to do this, 
or if there is a way to do it with refs (?)
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $kg$ & mass\\
        $m_mat$ & $kg$ & The size at which 50\% of the population is mature.\\ 
        \hline
    \end{tabular}
\end{table}

>>>>

Searching individuals:
\begin{equation} \label{eq:searching}
    \frac{dS}{dt} = aS -bS^2 - \frac{cS}{1+O} - eS - gO + fO
\end{equation}
Occupying individuals
\begin{equation} \label{eq:occupying}
    \frac{dO}{dt} = \frac{cS}{1+O} - eO - fO
\end{equation}

$aS - bS^2$ is individuals becoming mature.\\
$\frac{cS}{1+O}$ is searching individuals becoming occupiers through finding nests that are unoccuied.\\
$e$ is metabolic death rate\\
$f$ is the abandon rate\\
$g$ is the rate at which occupiers die in a contest\\

@@

\subsection{Contest Algorithm}
See Fig. \ref{fig:contests}.
For a defender $x_{def}$ vs an attacker $x_{atk}$, there are 3 stages:
each individual has an aggression trait $a$ and a mass $m$.
\begin{equation}\label{eq:logit}
    logit^{-1}(\alpha) = \frac{exp(\alpha)}{1 + exp(\alpha)}
\end{equation}

@@

I am not sure if this is the best way to do this, the tables in plant are more aesthetic. 
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $kg$ & mass\\
        $m_mat$ & $kg$ & The size at which 50\% of the population is mature.\\ 
        \hline
    \end{tabular}
\end{table}
